---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zomator

<!-- badges: start -->
<!-- badges: end -->

Zomator serves as a wraper function for the Zomato API. Zomator serves as a wraper function for the Zomato API. The functionality of this package is quite consistent with that of the [Zomato API documentation](https://developers.zomato.com/documentation?lang=id#/). The function format is `get_ <endpoint>`. The resulting overall output is tibble by considering the principle of [data tidy](https://vita.had.co.nz/papers/tidy-data.pdf).

## Installation

You can install the released version of zomator from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("zomator")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("technaut-education/zomator")
```
## Get API Keys

To create an API key, you can visit the [Zomato API website](https://developers.zomato.com/api?lang=id#headline2). The registration process is quite easy, we only need to register the email we have and confirm via the link sent by Zomato to our email. 

In general, we can make requests as many as 1000 times per day.


## Authentication

To perform authentication, we need to copy the api key we have obtained into our R environment. The trick is to run the following command:

```{r}
library(zomator)
```

```{r, eval=FALSE}
set_api_key(path = "./.Renviron")
```

In this function, we add a path where we will store our API key. Based on the command executed, we save the file `.Renviron` to the R working directory. Paste the api key in the window that appears.

## Get list of Categories

Get a list of categories can be obtain using `get_categories` function. List of all restaurants categorized under a particular restaurant type can be obtained using `get_search` function with `categories_id` as inputs.

```{r, cache=TRUE}
get_categories()
```

## Get city details

Find the Zomato ID and other details for a city . You can obtain the Zomato City ID in one of the following ways:

* City Name in the Search Query (`q`) - Returns list of cities matching the query
* Using coordinates (`lat` and `lon`) - Identifies the city details based on the coordinates of any location inside a city

If you already know the Zomato City ID, this API can be used to get other details of the city.

```{r, cache=TRUE}
get_cities(q = "Jakarta")
```


```{r, cache=TRUE}
# get New York City details using city_ids
get_cities(city_ids = 280)
```

## Get Zomato collections in a city

`get_collections` function can be used to obtain Zomato Restaurant Collections in a City. The location/City input can be provided in the following ways -

* Using Zomato City ID
* Using coordinates of any location within a city

List of all restaurants listed in any particular Zomato Collection can be obtained using the `get_search` function with Collection ID and Zomato City ID as the input.

```{r, cache=TRUE}
get_collections(city_id = 74)
```


## Get list of all cuisines in a city

`get_cuisines` function can be used to obtain all cuisines of restaurants listed in a city. The location/city input can be provided in the following ways -

* Using Zomato City ID
* Using coordinates of any location within a city

List of all restaurants serving a particular cuisine can be obtained using `get_search` function with cuisine ID and location details.

```{r, eval=FALSE}
get_cuisines(city_id = 280)
```

## Get list of restaurant types in a city

`get_establishments` function can be used to get a list of restaurant types in a city. The location/City input can be provided in the following ways -

* Using Zomato City ID
* Using coordinates of any location within a city

List of all restaurants categorized under a particular restaurant type can obtained using `get_search` function with Establishment ID and location details as inputs.


```{r, eval=FALSE}
get_establishments(city_id = 280)
```

## Get location details based on coordinates

Get Foodie and Nightlife Index, list of popular cuisines and nearby restaurants around the given coordinates.

```{r, eval=FALSE}
get_geocode(lat = 40.742051, lon = -74.004821)
```

## Get Zomato location details

Get Foodie Index, Nightlife Index, Top Cuisines and Best rated restaurants in a given location.

```{r, eval=FALSE}
get_location_details(entity_id = 36932, entity_type = "group")
```

## Search for locations

Search for Zomato locations by keyword. Provide coordinates to get better search results.

```{r, eval=FALSE}
get_locations(query = "Jakarta")
```


## Get daily menu of a restaurant

```{r, eval=FALSE}

get_dailymenu(res_id = 16782899)

```

## Get restaurant details

Get detailed restaurant information using Zomato restaurant ID. Partner Access is required to access photos and reviews.

```{r, cache=TRUE}
get_restaurant(res_id = 16782899)
```


## Get restaurant reviews

Get restaurant reviews using the Zomato restaurant ID. Only 5 latest reviews are available under the Basic API plan.


```{r, cache=TRUE}
get_reviews(res_id = 16782899)
```


## Search for restaurants

The location input can be specified using Zomato location ID or coordinates. Cuisine / Establishment / Collection IDs can be obtained from respective api calls. Get up to 100 restaurants for free API. Partner Access is required to access photos and reviews.

Examples:

* To search for 'Italian' restaurants in 'Manhattan, New York City', set cuisines = 55, entity_id = 94741 and entity_type = zone

```{r, cache=TRUE}
get_search(cuisines = 55, entity_id = 94741, entity_type = "zone")
```

* To search for 'cafes' in 'Manhattan, New York City', set establishment_type = 1, entity_type = zone and entity_id = 94741

```{r, cache=TRUE}
get_search(establishment_type = 1, entity_type = "zone", entity_id = 94741)
```


* Get list of all restaurants in 'Trending this Week' collection in 'New York City' by using entity_id = 280, entity_type = city and collection_id = 1

```{r, cache=TRUE}
get_search(entity_id = 280, entity_type = "city", collection_id = 1)
```







